Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-08-21 draftfinalreport_v4.Rnw
minor edits and todo notes

@@

@@

\begin{table}[htdp]
\begin{center}
<<include=FALSE,echo=FALSE,results=tex>>=
  PopnImmunityAll <- read.csv("data/PopnImmunityAll.csv") %>%
                       mutate(YS=2013-AgeEnd, YE=2013-AgeStart) %>%
                       mutate(YOB=ifelse(YS==YE,YS,ifelse(is.finite(YS), paste(YS,YE,sep="--"), paste0("<", YE)))) %>%
                       select("Year of Birth"=YOB, "Proportion Immune"=Immunity)
  print(xtable(PopnImmunityAll, align=rep("c",3)), include.rownames=F, floating=FALSE)
@
\end{center}
\caption{Vaccination coverage (2006--2013 years) and serosurvey estimates of immunity ($<2006$ birth cohorts) among different age classes used in these analyses, as provided by the Ministry of Health up to 1st January 2014. Note these values are from vaccination records and serosurveys. Vaccine efficacy for 0--4 year olds was 96\%, 5--13 year olds 99\%, and for $\geq$ 14 year olds equivocal serological results were considered non-immune. Note that 28\% of those $<1$ were considered immune due to passive immunity, following \citep{waaijenborg}.}
\label{table:sero}
\end{table}%

@@

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{figures/dob_vacc_dose.pdf}
\end{center}
\caption{The year of birth for those vaccinated with measles, mumps, and rubella (MMR) dose 1 is shown in the upper panel, MMR dose 2 the lower panel.}
\label{fig:yearandvacf}
\end{sidewaysfigure}

@@

@@

\subsection{Measles importation risk results}

@@

@@

>>>>

%%%%%%%%% TODO %%%%%%%%%%%%%%%%%%% ABOVE TABLE %%%%%%%%%%%%%%%%%%%%%%
%%%% find out why 'Cases' col name appears as 'Cases 1' %%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% check if \tiny means the page # is outside the table %%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%% TODO %%%%%%%%%%%%%%%%%%% ABOVE TABLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% double check what the intercept is (age0-2:euro:nzdep1-3?) w JM %%%%%%%%%%%%%
%%%%%%%%%%%%%% add to the caption text %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{table}[htdp]
\begin{center}
<<include=FALSE,echo=FALSE,results=tex>>=
  PopnImmunityAll <- read.csv("data/PopnImmunityAll.csv") %>%
                       mutate(YS=2013-AgeEnd, YE=2013-AgeStart) %>%
                       mutate(YOB=ifelse(YS==YE,YS,ifelse(is.finite(YS), paste(YS,YE,sep="--"), paste0("<", YE)))) %>%
                       select("Year of Birth"=YOB, "Proportion Immune"=Immunity)
  print(xtable(PopnImmunityAll, align=rep("c",3)), include.rownames=F, floating=FALSE)
@
\end{center}
\caption{Vaccination coverage (2006--2013 years) and serosurvey estimates of immunity ($<2006$ birth cohorts) among different age classes used in these analyses, as provided by the Ministry of Health up to 1st January 2014. Note these values are from vaccination records and serosurveys. Vaccine efficacy for 0--4 year olds was 96\%, 5--13 year olds 99\%, and for $\geq$ 14 year olds equivocal serological results were considered non-immune. Note that 28\% of those $<1$ were considered immune due to passive immunity, following \citep{waaijenborg}.\Sexpr{naive_percent}\% of the overall population of New Zealand are thereforecurrently considered to be immunologically na\"{\i}ve to measles.}
\label{table:sero}
\end{table}%

@@

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{figures/dob_vacc_dose.pdf}
\end{center}
\caption{The year of birth for those measles cases vaccinated with measles, mumps, and rubella (MMR) dose 1 is shown in the upper panel, MMR dose 2 the lower panel.}
\label{fig:yearandvacf}
\end{sidewaysfigure}

@@

%%%%%%%%% TODO %%%%%%%%%%%%%%%%%%% ABOVE TEXT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%% NIGEL DISLIKES ALL THE HYPERLINKS - CHANGE TO 'Figures 26--37' ? %%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Measles importation risk results}
%%%%%%%%% TODO %%%%%%%%%%%%%%%%%%% BELOW 'RISK' TABLES and FIGURES %%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%% CHECK UNITS FOR RISK ARE 'CASES PER MILLION TRAVELLERS PER YEAR' %%%%%%%%
%%% was annual incidence per million * # travellers per year %%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%% TODO %%%%%%%%%%%%%%%%%%% BELOW 'RISK' TABLES and FIGURES %%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%% ADD UNITS FOR RISK TO CAPTIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%% TODO %%%%%%%%%%%%%%%%%%% ABOVE/BELOW RE REGRESSION %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%% NF COMMENT - WHAT'S THE AIM OF THE REGRESSION - PARSIMONIOUS MODEL? %%%%%
%%%%%%%%%%%%%%% good point! NOT SURE TC DID AND I LEFT IN %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%% but %%%%%%%%%%%%% MAYBE IGNORE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%% TODO %%%%%%%%%%%%%%%%%%% ABOVE RE REGRESSION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%% NF COMMENT - COSTS CALCULATED FROM DATA, SO NOT INDEPENDENT %%%%%%%%%%%%%%
%%%%%%%%%%%%%%% good point! NOT SURE TC DID AND I LEFT IN %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%% but %%%%%%%%%%%%% MAYBE IGNORE AGAIN %%%%%%%%%%%%%%%%%%%%%%%%
